Area maximisation in continuous time

### 2018-03-12 Notes/ContTime.tex
typo
markov bib file in notes
laplace envelope notes
laplace envelope w/o topology constraints & homeostatic
chernoff etc

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
% arXiv Paper ************************************************
%
% Subhaneil Lahiri's template
%
% Before submitting:
%    Comment out hyperref
%    Comment out showkeys
%    Replace \input{mydefs.tex} with its contents
%       or include mydefs.tex in zip/tar file
%    Replace \input{newsymb.tex} with its contents
%       or include newsymb.tex in zip/tar file
%    Put this file, the .bbl file, any picture or
%       other additional files and natbib.sty
%       file in a zip/tar file
%
% **** -----------------------------------------------------------
\documentclass[12pt]{article}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
%
% >> Only for drafts! <<
\usepackage[notref,notcite]{showkeys}
% ----------------------------------------------------------------
%\numberwithin{equation}{section}
%\renewcommand{\baselinestretch}{1.5}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
\newcommand{\inv}{^{-1}}
\newcommand{\dg}{^\mathrm{dg}}
\newcommand{\trans}{^\mathrm{T}}
\newcommand{\I}{\mathbf{I}}
%vec of ones
\newcommand{\onev}{\mathbf{e}}
%mat of ones
\newcommand{\onem}{\mathbf{E}}
%Markov matrix
\newcommand{\MM}{\mathbf{Q}}
%equilibrium distribution
\newcommand{\eq}{\mathbf{p}^\infty}
%first passage times
\newcommand{\fpt}{\mathbf{T}}
%off-diag first passage times
\newcommand{\fptb}{\overline{\fpt}}
%fundamental matrix
\newcommand{\fund}{\mathbf{Z}}
%other symbols
\newcommand{\Pb}{\mathbf{P}}
\newcommand{\D}{\mathbf{D}}
\newcommand{\pib}{\boldsymbol{\pi}}
\newcommand{\Lb}{\boldsymbol{\Lambda}}
\newcommand{\w}{\mathbf{w}}
\newcommand{\uv}{\mathbf{u}}
\newcommand{\vv}{\mathbf{v}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\enc}{\mathbf{q}}
\newcommand{\frg}{\W^{\mathrm{F}}}
\newcommand{\F}{\boldsymbol{\Phi}}
\DeclareMathOperator{\SNR}{SNR}
\DeclareMathOperator{\snr}{SNR}
\DeclareMathOperator{\env}{Env}
\newcommand{\rh}{\hat{r}}
\newcommand{\CI}{\mathcal{I}}
\newcommand{\CS}{\mathcal{S}}
\newcommand{\CA}{\mathcal{A}}
\newcommand{\CB}{\mathcal{B}}
\newcommand{\comp}{^\mathrm{c}}
% ----------------------------------------------------------------
\input{sl_theorems_preamble.tex}
% ----------------------------------------------------------------
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title info:
\title{Area maximisation in continuous time}
%
% Author List:
%
\author{Subhaneil Lahiri
%
}

@@

Then, defining
%
\begin{equation}\label{eq:eigdiff}
  F_{ab} = \left\{
           \begin{aligned}
             &rt\,\e^{-q_art}, &\quad&\text{if } q_a=q_b,\\
             &\frac{\e^{-q_art}-\e^{-q_brt}}{q_b-q_a}, &&\text{otherwise,}
           \end{aligned}
           \right.
\end{equation}
%
we get
%
\begin{equation}\label{findiff}
\begin{aligned}
  \pdiff{\CL}{\M^\pm_{gh}} =&\,
    f^\pm \eq_g \prn{\brk{\fund \, \enc \, \e^{rt\frg} \w}_h - \brk{\fund \, \enc \, \e^{rt\frg} \w}_g} \\
    &\pm \eq_g \prn{\brk{\e^{rt\frg} \w}_h - \brk{\e^{rt\frg} \w}_g} \\
    &+ f^\pm \sum_{ab} F_{ab} (\eq\enc\uv^a) \vv^a_g (\uv^b_h-\uv^b_g) (\vv^a\w) \\
    &+ \mu^\pm_{gh} - \mu^\pm_{gg}.
\end{aligned}
\end{equation}
%

@@

In analogy to \eqref{eq:funddef}, define
%
\begin{equation}\label{eq:lfund}
  \fund(s) = (s\I +\onev\pib -\MM)\inv.
\end{equation}
%
This reduces to the fundamental matrix at $s=0$.
The analogous result to \eqref{eq:fundrowsum} is
%
\begin{equation}\label{eq:lfundrowsum}
  \fund(s)\onev = \frac{\tau}{1+s\tau}\onev.
\end{equation}
%
The analogues of \eqref{eq:fundprob}, \eqref{eq:fundQZ} and \eqref{eq:fundZQ} are much uglier, but luckily we won't need them.
Supose we have some row vector $\mathbf{a}$ such that $\mathbf{a}\onev=0$.
Then $\mathbf{a}\fund(s)$ is independent of $\pib$:
%
\begin{equation}\label{eq:alfund}
  \pdiff{(\mathbf{a}\fund(s))_i}{\pib_k} = (\mathbf{a}\fund(s)\onev) \fund_{ki}(s) = \frac{\tau}{1+s\tau} (\mathbf{a}\onev) \fund_{ki}(s) = 0.
\end{equation}
%

@@

The resulting SNR curve and envelope are
%
\begin{equation}\label{eq:env}
  \snr(t) = \frac{\sqrt{N}\,\e^{(s_0-1/t_0)t}}{C'(s_0)},
  \qquad
  \snr(t_0) = \sqrt{N}\env(t_0) = \frac{\sqrt{N}\,\e^{s_0t_0-1}}{C'(s_0)}
   = \frac{\sqrt{N}\,B(s)\e^{s_0t_0-1}}{t_0},
\end{equation}
%
where $s_0$ is a function of $t_0$ determined by \eqref{eq:envs0t0}.

@@

\bibliographystyle{utcaps_sl}
\bibliography{maths,neuro}

>>>>

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
% arXiv Paper ************************************************
%
% Subhaneil Lahiri's template
%
% Before submitting:
%    Comment out hyperref
%    Comment out showkeys
%    Replace \input{?.tex} with its contents
%       or include ?.tex in zip/tar file
%    Put this file, the .bbl file, any picture or
%       other additional files and natbib.sty
%       file in a zip/tar file
%
% **** -----------------------------------------------------------
\documentclass[12pt]{article}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
%
% >> Only for drafts! <<
\usepackage[notref,notcite]{showkeys}
% ----------------------------------------------------------------
%\numberwithin{equation}{section}
%\renewcommand{\baselinestretch}{1.5}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
%vec of ones
\newcommand{\onev}{\mathbf{e}}
%mat of ones
\newcommand{\onem}{\mathbf{E}}
%Markov matrix
\newcommand{\MM}{\mathbf{Q}}
%equilibrium distribution
\newcommand{\eq}{\mathbf{p}^\infty}
%first passage times
\newcommand{\fpt}{\mathbf{T}}
%off-diag first passage times
\newcommand{\fptb}{\overline{\fpt}}
%fundamental matrix
\newcommand{\fund}{\mathbf{Z}}
%other symbols
\newcommand{\Pb}{\mathbf{P}}
\newcommand{\D}{\mathbf{D}}
\newcommand{\pib}{\boldsymbol{\pi}}
\newcommand{\Lb}{\boldsymbol{\Lambda}}
\newcommand{\w}{\mathbf{w}}
\newcommand{\uv}{\mathbf{u}}
\newcommand{\vv}{\mathbf{v}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\enc}{\mathbf{q}}
\newcommand{\frg}{\W^{\mathrm{F}}}
\newcommand{\F}{\boldsymbol{\Phi}}
\DeclareMathOperator{\SNR}{SNR}
\DeclareMathOperator{\snr}{SNR}
\DeclareMathOperator{\env}{Env}
\newcommand{\rh}{\hat{r}}
\newcommand{\CA}{\mathcal{A}}
\newcommand{\CB}{\mathcal{B}}
% ----------------------------------------------------------------
\input{sl_theorems_preamble.tex}
% ----------------------------------------------------------------
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title info:
\title{Area maximisation in continuous time}
%
% Author List:
%
\author{Subhaneil Lahiri
%
}

@@

Then, defining
%
\begin{equation}\label{eq:eigdiff}
  F_{ab} = \left\{
           \begin{aligned}
             &rt\,\e^{-q_art}, &\quad&\text{if } q_a=q_b,\\
             &\frac{\e^{-q_art}-\e^{-q_brt}}{q_b-q_a}, &&\text{otherwise,}
           \end{aligned}
           \right.
\end{equation}
%
we get
%
\begin{equation}\label{findiff}
\begin{aligned}
  \pdiff{\CL}{\M^\pm_{gh}} =&\,
    f^\pm \eq_g \prn{\brk{\fund \, \enc \, \e^{rt\frg} \w}_h - \brk{\fund \, \enc \, \e^{rt\frg} \w}_g} \\
    &\pm \eq_g \prn{\brk{\e^{rt\frg} \w}_h - \brk{\e^{rt\frg} \w}_g} \\
    &+ f^\pm \sum_{ab} F_{ab} (\eq\enc\uv^a) \vv^a_g (\uv^b_h-\uv^b_g) (\vv^b\w) \\
    &+ \mu^\pm_{gh} - \mu^\pm_{gg}.
\end{aligned}
\end{equation}
%

@@

In analogy to \eqref{eq:funddef}, define
%
\begin{equation}\label{eq:lfund}
  \fund(s) = (s\I +\onev\pib -\MM)\inv.
\end{equation}
%
This reduces to the fundamental matrix at $s=0$.
The analogous result to \eqref{eq:fundrowsum} is
%
\begin{equation}\label{eq:lfundrowsum}
  \fund(s)\onev = \frac{\tau}{1+s\tau}\onev.
\end{equation}
%
The analogues of \eqref{eq:fundprob}, \eqref{eq:fundQZ} and \eqref{eq:fundZQ} are much uglier, but luckily we won't need them.
Supose we have some row vector $\mathbf{a}$ such that $\mathbf{a}\onev=0$.
Then $\mathbf{a}\fund(s)$ is independent of $\pib$:
%
\begin{equation}\label{eq:alfund}
  \pdiff{(\mathbf{a}\fund(s))_i}{\pib_k} = -(\mathbf{a}\fund(s)\onev) \fund_{ki}(s) = -\frac{\tau}{1+s\tau} (\mathbf{a}\onev) \fund_{ki}(s) = 0.
\end{equation}
%

@@

The resulting SNR curve and envelope are
%
\begin{equation}\label{eq:env}
  \snr(t) = \frac{\sqrt{N}\,\e^{(s_0-1/t_0)t}}{C'(s_0)},
  \qquad
  \snr(t_0) = \sqrt{N}\env(t_0) = \frac{\sqrt{N}\,\e^{s_0t_0-1}}{C'(s_0)}
   = \frac{\sqrt{N}\,B(s_0)\e^{s_0t_0-1}}{t_0},
\end{equation}
%
where $s_0$ is a function of $t_0$ determined by \eqref{eq:envs0t0}.

@@

\bibliographystyle{utcaps_sl}
\bibliography{maths,neuro,markov}
